---
title: "Rudd_Exc1"
author: "Jacob Rudd"
format: html
---

title: "Exercise 1"
author: "Jacob Rudd"
format: "Html" 

```{r}
getwd()
```

```{r}
library("haven")
library("tidyverse")
library("foreign")
qog_ei_ts_sept21 <-read_dta("~/Downloads/qog_ei_ts_sept21.dta")
summary(qog_ei_ts_sept21)
my_data <- read_dta("~/Downloads/qog_ei_ts_sept21.dta")
mean(my_data$wdi_fossil, na.rm = TRUE)
```

#Regarding the average of wdi_fossil, 65.53438 indicates the average fossil fuel consumption as a percentage of total energy consumption across the set of units (country,year) analyzed in the data. I assume this would then mean that the average takes into account the percentage aggregated over time (although not necessarily change over time), as well as across countries. 

#Description: The data set attempts to measure countries' environmental performance over time. Hence, it contains data items such as existence and degree of environmental policies, public opinion in relation to environment, and degree of country-pressure on the environment. Also contains general information such as average annual rainfall. 

#Unit of Analysis: I believe the unit of analysis is country, year. So for example, (Afghanistan, 2006) Or maybe, (2006, Afghanistan)


